\documentclass[10pt]{article}
\usepackage[hmargin=1in, top=0.5in, bottom = 0.85in, centering]{geometry}
\usepackage{graphicx}
\usepackage{float}
\usepackage{multirow}
\usepackage{caption}
\usepackage[labelformat=simple]{subcaption}
\usepackage{parskip}
\usepackage{mathtools}
\usepackage{color}


\begin{document}

\section{270K Bone Marrow Dataset on Cloud}

\paragraph{}
Seurat 3.1.0 \qquad vs \qquad SCANPY 1.4.4.post1 \qquad vs \qquad Cumulus 0.10.0

\begin{table}[H]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		Analysis & Seurat v3 & SCANPY & Cumulus\\
		\hline \hline
		Count matrix aggregation & N/A & N/A & $6$ sec   \\
		\hline
		HVG selection & $1$ min $6$ sec & $1$ min $46$ sec  & $15$ sec   \\
		\hline
		Batch correction & $22$ h $34$ min  & $14$ min $34$ sec  & $25$ sec  \\
		\hline
		PCA & $9$ min $13$ sec  & $26$ sec  & $16$ sec  \\
		\hline
		Find K nearest neighbors & $8$ min $43$ sec   & --   & $13$ sec  \\
		\hline
		Louvain-like clustering & $39$ min $50$ sec  & $1$ h $7$ min  & $1$ min $48$ sec   \\
		\hline
		t-SNE-based visualization & $3$ min $7$ sec  & $21$ min $47$ sec  & $2$ min $40$ sec  \\
		\hline
		UMAP-based visualization & $17$ min $33$ sec  & $17$ min $25$ sec   & $3$ min $7$ sec  \\
		\hline
		DE analysis \& Annotation & $2$ h $15$ min & $2$ min & $2$ min $4$ sec  \\
		\hline \hline
		\textbf{Overall} & $26$ h $8$ min & $2$ h $5$ min & $10$ min $54$ sec ($37$ min)  \\
		\hline
	\end{tabular}
\end{table}

\paragraph{}
The benchmark was taking on Google Cloud server with 32 CPUs (Intel Broadwell platform) and 120GB memory. Cumulus was done via Terra workflow, while SCANPY and Seurat v3 were through VM instances.

\begin{itemize}
	\item
	For Seurat v3, Batch correction step was done with 2 cores using R \textit{future} package. This is because the benchmark failed when assigning 10, 15, 20, or 32 cores. So we decide to set it to 2 to make sure it can finish.
	\par
	Besides, the batch correction was on 8 individuals, not the original 63 batches. This is because taking 63 batches for correction would fail due to limit of R vector length.
\par
For all the other steps, the benchmark was done under 32 cores using R \textit{future} package. Besides, t-SNE-based visualization step used 32 cores which was set by \textit{mc.cores}, not \textit{future}.

	\item
	SCANPY benchmark uses BBKNN for batch correction. That's why it doesn't have the ``Find K nearest neighbors" step stat.

	\item
	Cumulus has 2 overall time results. $37$ minutes is the overall time including IO, and Terra's pre- and postprocessing, while $10$ min $54$ sec is the time spent on analysis.
\end{itemize}
\paragraph{}




\end{document}